Automated Topic Naming

### 2012-01-19 ese/ese.tex
- [X] Different clustering algorithms result in different trees:      how sensitive the results were to algorithm/distance measure      choices?

Two perspectives used to evaluate multi-label learners are with micro or macro measurements (shown in Figure \ref{fig:mulan}a).
Macro measurements are aggregated at a class or label level (per class) while micro measurements are at the element level (per element).
A macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. 
For MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels.%, see Figure \ref{fig:mulan}.

@@

Using this space, we first conducted pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair. We
found that in $3/10$ of these tests, the two developers were significantly
different (i.e. distant in the 7-d space). This implies
that there are developers who focus on different NFRs or different
proportions of NFRs.

@@

\begin{table}
\begin{tabular}{l|c}
\toprule
\textbf{NFR} & \textbf{Developer} \\
\midrule
\emph{Usability} & \texttt{dennis, neilc} \\
\emph{Portability} & \texttt{scrappy, meskes} \\
\emph{Efficiency} & \texttt{inoue, neilc} \\
\emph{Reliability} & \texttt{jurka, joe} \\
\emph{Functionality} & \texttt{thomas, weick} \\
\emph{Maintainability} & \texttt{scrappy, ishii}\\
\bottomrule
\end{tabular}
	\caption{Developer interest in NFRs}
	\label{tbl:devinterest}
\end{table}

>>>>

Two perspectives used to evaluate multi-label learners are with micro or macro measurements (shown in Figure \ref{fig:mulan}a).
Macro measurements are aggregated at a class or label level (per class) while micro measurements are at the element level (per element).
A macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. 
For MaxDB, the macro-ROC values are undefined because of poor
performance of one of the labels.%, see Figure \ref{fig:mulan}. 
During cross-folds validation if the class imbalance or poor learner
performance causes a division by zero when evaluating one of the NFR
labels (in this case \emph{usability}), creating an undefined
value. This undefined 
value is propagated through to the mean of ROC per NFR label, causing
the end calculation of macro-ROC to be undefined.

@@

Using this space, we first conducted pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer 
 pair on their
NFR distributions
(18 developers, 306 pair-wise tests).
We
found that in $27\%$ of these tests, the two developers were significantly
different (i.e. distant in the 7-d space and have significant p-values less than $0.05$). This implies
that there are developers who focus on different NFRs or different
proportions of NFRs, but the majority of developers have similar NFR distributions.

@@

\begin{table}
\centering
\begin{tabular}{l|c}
\toprule
\textbf{NFR} & \textbf{Developer} \\
\midrule
\emph{Usability} & \texttt{dennis, neilc} \\
\emph{Portability} & \texttt{scrappy, meskes} \\
\emph{Efficiency} & \texttt{inoue, neilc} \\
\emph{Reliability} & \texttt{jurka, joe} \\
\emph{Functionality} & \texttt{thomas, weick} \\
\emph{Maintainability} & \texttt{scrappy, ishii}\\
\bottomrule
\end{tabular}
	\caption{Developer interest in NFRs}
	\label{tbl:devinterest}
\end{table}

Based on Figure \label{fig:authorsim} we wanted to see which clusters
\texttt{momjian}, \texttt{tgl}, and \texttt{petere} would be in if we
evaluated the clusters proportionately, that is if we use distance
measures that normalize the data and ignore magnitude (e.g. turning an
author NFR contributions into a histogram or unit-vector) such as
cosine distance, euclidean distance of unit vectors, or Pearson
correlation. Euclidean distance uses both angle and magnitude of a
vector. For all 3 non-magnitude distances measures we tend to see that
the 3 largest contributors, \texttt{momjian}, \texttt{tgl}, and
\texttt{petere} inhabit the same clusters when we use 2 clusters or 6
clusters. This confirms the observations in
Figure \label{fig:authorsim}, which uses Pearson correlation, that the larger contributors tend to be
proportionally similar.
